---
title: "RESTORES Manusript"
output:
  pdf_document: default
  html_document: default
---


```{r, message=FALSE, echo = FALSE, warning=FALSE}

## Clear Workspace ##
rm(list = ls())

## Load Libraries ##
library(tidyverse)
library(tibbleOne)
library(magrittr)
library(labelled)
library(knitr)
library(kableExtra)
library(readxl)
library(qwraps2)
library(lme4)
library(emmeans)
library(glue)

knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)

sites_to_include <- c(2)

restores_inclusion <- read_xlsx('data/RESTORES Randomized.xlsx')

# ids_to_include <- restores_inclusion %>% 
#   filter(withdrew == 'NO') %>% 
#   pull(patient_id)

## Load Analysis Data Sets ##

.proc_restores <- function(data){
  
  # setting visit as a factor
  mutate(
    data,
    visit = factor(
      visit, 
      levels = 1:3, 
      labels = c("Baseline", "Week 6", "Week 12")
    ), 
    pt_group = factor(
      pt_group,
      levels = c("B", "C", "A")
    )
  ) %>% 
  arrange(patient_id, visit) %>% 
  group_by(patient_id) 
  
}

restores_1 <- read_xlsx("data/RESTORES 1.xlsx") %>% 
  filter(
    visit > 0, 
    # patient_id %in% ids_to_include,
    site %in% sites_to_include
  ) %>% 
  .proc_restores()
  

# create one column for each variable in
# make_bl_vals that contains baseline value
make_bl_vals <- names(restores_1)[-c(1:10)]

restores_1 <- restores_1 %>% 
  mutate_at(make_bl_vals, .funs = list(at_bl = function(x) x[1]))

```

# Table 4 
## Variables only applicable to UAB: Total Cholesterol, HDL Choloesterol, LDL Cholesterol, & Triglycerides

**NOTE** The results include participants from site(s) `r glue_collapse(sites_to_include, sep = ' and ' )`

```{r}

outcomes <- c(
  "total_cholesterol",
    "hdl_cholesterol",
    "ldl_cholesterol",
    "triglyerides"
)

source("R/within_group_diffs.R")

outcomes %>% 
  purrr::set_names() %>% 
  map_dfr(
    .f = ~ within_group_diffs_by_visit(
      data = restores_1, 
      outcome = .x
    ),
    .id = 'variable'
  ) %>% 
  select(-starts_with("vis")) %>% 
  rename(Variable = variable) %>% 
  kable() %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::add_header_above(
    header = c(' ' = 1, "Difference (95% CI) from Baseline to Week 12" = 3)
  )


```


```{r}

sites_to_include <- c(1,2)

## Load Analysis Data Sets ##

restores_1 <- read_xlsx("data/RESTORES 1.xlsx") %>% 
  filter(
    visit > 0, 
    # patient_id %in% ids_to_include,
    site %in% sites_to_include
  ) %>% 
  .proc_restores() 

# create one column for each variable in
# make_bl_vals that contains baseline value
make_bl_vals <- names(restores_1)[-c(1:10)]

restores_1 <- restores_1 %>% 
  mutate_at(make_bl_vals, .funs = list(at_bl = function(x) x[1]))

```

# Table 4 (Continued I)

**NOTE** The results include participants from site(s) `r glue_collapse(sites_to_include, sep = ' and ' )`

```{r}

outcomes <-
  c(
    "blood_glucose",
    "blood_urea_nitrogen",
    "blood_creatinine",
    "blood_chloride",
    "blood_co2",
    "Calcium__mg_",
    "blood_protein",
    "blood_albumin",
    "blood_globulin",
    "blood_bilirubin",
    "blood_alk_phosph",
    "blood_ast",
    "blood_alt"
  )

outcomes %>% 
  purrr::set_names() %>% 
  map_dfr(
    .f = ~ within_group_diffs_by_visit(
      data = restores_1, 
      outcome = .x
    ),
    .id = 'variable'
  ) %>% 
  select(-starts_with("vis")) %>% 
  kable() %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::add_header_above(
    header = c(' ' = 1, "Difference (95% CI) from Baseline to Week 12" = 3)
  )

```


```{r}

sites_to_include <- c(1,2)

## Load Analysis Data Sets ##

restores_1 <- read_xlsx("data/RESTORES 1.xlsx") %>%
  select(
    patient_id,
    age,
    gender
  ) %>%
  group_by(patient_id) %>%
  filter(row_number()==1)

restores_2 <- read_csv("data/RESTORES 2.csv") %>% 
  filter(
    visit > 0, 
    # patient_id %in% ids_to_include,
    site %in% sites_to_include
  ) %>% 
  # setting visit as a factor
  .proc_restores() %>% 
  left_join(restores_1, by = 'patient_id')

# create one column for each variable in
# make_bl_vals that contains baseline value
make_bl_vals <- names(restores_2)[-c(1:10)]

restores_2 <- restores_2 %>% 
  mutate_at(make_bl_vals, .funs = list(at_bl = function(x) x[1]))

```


# Table 4 (Continued II)

**NOTE** The results include participants from site(s) `r glue_collapse(sites_to_include, sep = ' and ' )`

```{r}

outcomes <- c("Calcium__mg", "Sodium__mg", "Potassium__mg")

outcomes %>% 
  purrr::set_names() %>% 
  map_dfr(
    .f = ~ within_group_diffs_by_visit(
      data = restores_2, 
      outcome = .x
    ),
    .id = 'variable'
  ) %>% 
  select(-starts_with("vis")) %>% 
  kable() %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::add_header_above(
    header = c(' ' = 1, "Difference (95% CI) from Baseline to Week 12" = 3)
  )

```


```{r}

sites_to_include <- c(1,2)

## Load Analysis Data Sets ##

restores_1 <- read_xlsx("data/RESTORES 1.xlsx") %>% 
  filter(
    # patient_id %in% ids_to_include,
    site %in% sites_to_include
  ) %>% 
  # setting visit as a factor
  mutate(
    visit = factor(
      visit, 
      levels = 0:3, 
      labels = c("Screening","Baseline", "Week 6", "Week 12")
    ), 
    pt_group = factor(
      pt_group,
      levels = c("B", "C", "A")
    )
  ) %>% 
  arrange(patient_id, visit) %>% 
  group_by(patient_id) 

# create one column for each variable in
# make_bl_vals that contains baseline value
make_bl_vals <- names(restores_1)[-c(1:10)]

restores_1 <- restores_1 %>% 
  mutate_at(make_bl_vals, .funs = list(at_bl = function(x) x[1]))

```

# Table 5

- The results include participants from site(s) `r glue_collapse(sites_to_include, sep = ' and ' )`
- Comparing Screening to week 12

```{r}

outcomes <- c("bp_sys", "bp_dia", "bmi", "waist_circumference")

outcomes %>% 
  purrr::set_names() %>% 
  map_dfr(
    .f = ~ within_group_diffs_by_visit_screening(
      data = restores_1, 
      outcome = .x
    ),
    .id = 'variable'
  ) %>% 
  select(-starts_with("vis")) %>% 
  kable() %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::add_header_above(
    header = c(' ' = 1, "Difference (95% CI) from Screening to Week 12" = 3)
  )

```

```{r}

sites_to_include <- c(2)

## Load Analysis Data Sets ##

restores_1 <- read_xlsx("data/RESTORES 1.xlsx") %>% 
  filter(
    # patient_id %in% ids_to_include,
    site %in% sites_to_include
  ) %>% 
  # setting visit as a factor
  mutate(
    visit = factor(
      visit, 
      levels = 0:3, 
      labels = c("Screening","Baseline", "Week 6", "Week 12")
    ), 
    pt_group = factor(
      pt_group,
      levels = c("B", "C", "A")
    )
  ) %>% 
  arrange(patient_id, visit) %>% 
  group_by(patient_id) 

# create one column for each variable in
# make_bl_vals that contains baseline value
make_bl_vals <- names(restores_1)[-c(1:10)]

restores_1 <- restores_1 %>% 
  mutate_at(make_bl_vals, .funs = list(at_bl = function(x) x[1]))

```


# Table 5 (Continued)

- The results include participants from site(s) `r glue_collapse(sites_to_include, sep = ' and ' )`
- Comparing Screening to week 12

```{r}

outcomes <- c("hip_circumference")

outcomes %>% 
  purrr::set_names() %>% 
  map_dfr(
    .f = ~ within_group_diffs_by_visit_screening(
      data = restores_1, 
      outcome = .x
    ),
    .id = 'variable'
  ) %>% 
  select(-starts_with("vis")) %>% 
  kable() %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::add_header_above(
    header = c(' ' = 1, "Difference (95% CI) from Screening to Week 12" = 3)
  )

```


```{r}

sites_to_include <- c(1,2)

## Load Analysis Data Sets ##

restores_1 <- read_xlsx("data/RESTORES 1.xlsx") %>%
  select(
    patient_id,
    age,
    gender
  ) %>%
  group_by(patient_id) %>%
  filter(row_number()==1)

restores_2 <- read_csv("data/RESTORES 2.csv") %>% 
  filter(
    visit > 0, 
    # patient_id %in% ids_to_include,
    site %in% sites_to_include
  ) %>% 
  # setting visit as a factor
  .proc_restores() %>% 
  left_join(restores_1, by = 'patient_id')

# create one column for each variable in
# make_bl_vals that contains baseline value
make_bl_vals <- names(restores_2)[-c(1:5)]

restores_2 <- restores_2 %>% 
  mutate_at(make_bl_vals, .funs = list(at_bl = function(x) x[1]))

```


# Table 6

**NOTE** The results include participants from site(s) `r glue_collapse(sites_to_include, sep = ' and ' )`

```{r}

outcomes <- c("calories",	"protein",	"cho",	"fat",	"vit_c")

outcomes %>% 
  purrr::set_names() %>% 
  map_dfr(
    .f = ~ within_group_diffs_by_visit(
      data = restores_2, 
      outcome = .x
    ),
    .id = 'variable'
  ) %>% 
  select(-starts_with("vis")) %>% 
  kable() %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::add_header_above(
    header = c(' ' = 1, "Difference (95% CI) from Baseline to Week 12" = 3)
  )

```


```{r}

sites_to_include <- c(1,2)

## Load Analysis Data Sets ##

restores_1 <- read_xlsx("data/RESTORES 1.xlsx") %>%
  select(
    patient_id,
    age,
    gender
  ) %>%
  group_by(patient_id) %>%
  filter(row_number()==1)

restores_3 <- read_xlsx("data/RESTORES 3.xlsx") %>% 
  filter(
    visit > 0, 
    # patient_id %in% ids_to_include,
    site %in% sites_to_include
  ) %>% 
  # setting visit as a factor
  .proc_restores() %>% 
  left_join(restores_1, by = 'patient_id')

# create one column for each variable in
# make_bl_vals that contains baseline value
make_bl_vals <- names(restores_3)[-c(1:5)]

restores_3 <- restores_3 %>% 
  mutate_at(make_bl_vals, .funs = list(at_bl = function(x) x[1]))

```


# Table 7

**NOTE** The results include participants from site(s) `r glue_collapse(sites_to_include, sep = ' and ' )`

```{r}

outcomes <- c(
    "avg_step_counts",
    "sedentary_daily",
    "light_daily",
    "moderate_daily",
    "vigorous_daily",
    "very_vigorous_daily",
    "active_time_daily",
    "avg_wear_time_minutes"
  )

outcomes %>% 
  purrr::set_names() %>% 
  map_dfr(
    .f = ~ within_group_diffs_by_visit(
      data = restores_3, 
      outcome = .x
    ),
    .id = 'variable'
  ) %>% 
  select(-starts_with("vis")) %>% 
  kable() %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::add_header_above(
    header = c(' ' = 1, "Difference (95% CI) from Baseline to Week 12" = 3)
  )

```



```{r}

sites_to_include <- c(1,2)

## Load Analysis Data Sets ##

restores_1 <- read_xlsx("data/RESTORES 1.xlsx") %>% 
  filter(
    visit > 0, 
    # patient_id %in% ids_to_include,
    site %in% sites_to_include
  ) %>% 
  # setting visit as a factor
  .proc_restores() 

# create one column for each variable in
# make_bl_vals that contains baseline value
make_bl_vals <- names(restores_1)[-c(1:5)]

restores_1 <- restores_1 %>% 
  mutate_at(make_bl_vals, .funs = list(at_bl = function(x) x[1]))

```

# Supplementary Table 2

**NOTE** The results include participants from site(s) `r glue_collapse(sites_to_include, sep = ' and ' )`

```{r}

outcomes <- c(
    "tot_met_walked",
    "sppb_total",
    "mean_pt_knee_ext",
    "llfdi_ftot_scale",
    "llfdi_ltot_scale"
  )

outcomes %>% 
  purrr::set_names() %>% 
  map_dfr(
    .f = ~ within_group_diffs_by_visit(
      data = restores_1, 
      outcome = .x
    ),
    .id = 'variable'
  ) %>% 
  select(-starts_with("vis")) %>% 
  kable() %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::add_header_above(
    header = c(' ' = 1, "Difference (95% CI) from Baseline to Week 12" = 3)
  )

```




```{r}

sites_to_include <- c(2)

## Load Analysis Data Sets ##
restores_1 <- read_xlsx("data/RESTORES 1.xlsx") %>%
  select(
    patient_id,
    age,
    gender
  ) %>%
  group_by(patient_id) %>%
  filter(row_number()==1)

restores_2 <- read_xlsx("data/RESTORES 2.2.xlsx") %>% 
  filter(
    visit > 0, 
    # patient_id %in% ids_to_include,
    site %in% sites_to_include
  ) %>% 
  # setting visit as a factor
  mutate(
    visit = factor(
      visit, 
      levels = 1:3, 
      labels = c("Baseline", "Week 6", "Week 12")
    )
  ) %>% 
  arrange(patient_id, visit) %>% 
  group_by(patient_id) %>% 
  left_join(restores_1, by = 'patient_id')

# create one column for each variable in
# make_bl_vals that contains baseline value
make_bl_vals <- names(restores_2)[-c(1:5)]

restores_2 <- restores_2 %>% 
  mutate_at(make_bl_vals, .funs = list(at_bl = function(x) x[1]))
```

# Supplementary Table 3

**NOTE** The results include participants from site(s) `r glue_collapse(sites_to_include, sep = ' and ' )`

```{r}

outcomes <- c("leg_press", "chest_press", "knee_extension")

outcomes %>% 
  purrr::set_names() %>% 
  map_dfr(
    .f = ~ within_group_diffs_by_visit(
      data = restores_2, 
      outcome = .x
    ),
    .id = 'variable'
  ) %>% 
  select(-starts_with("vis")) %>% 
  kable() %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::add_header_above(
    header = c(' ' = 1, "Difference (95% CI) from Baseline to Week 12" = 3)
  )

```




